Instructions for developing new pages for the MarineOmics webpage

### 2023-12-13 DRAFT_DNA_methylation.Rmd
added methylation figure

## What to expect
DNA methylation at CpG locus can vary to 0-100%. Like wise methyation at the level Generally speaking in

>>>>

## What to expect
DNA methylation at CpG locus can vary to 0-100%. Like wise methylation at the gene level can vary and is commonly established as mean methylation level of CpG across gene, assuming some majority degree of gene coverage. Similarly with considering the methylation level of a given loci often time some threshold might be set as seen in code below. From an taxa perspective it can vary WIDELY on what to expect. The figure below shows

```{r meth-bp, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/meth_ratio.png")
```
